---
title: "auction_status"
author: "Andrew Martin"
date: "April 2, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r warning = FALSE, echo = FALSE, message = FALSE}
library(googlesheets)
library(janitor)
library(tidyverse)
library(devtools)
devtools::install_github('almartin82/projprep')
#devtools::install_local(path = '~/Google Drive/repositories/projprep')
suppressPackageStartupMessages(library(projprep))
```

## Get data from auction google sheet

```{r}

auction_url <- 'https://docs.google.com/spreadsheets/d/1v1k5gBTV3NoFvd4O68WdOstsF-NS22YrBvYv5sXzCIc/'

auction_result <- auction_url %>%
  googlesheets::gs_url() %>%
  googlesheets::gs_read(ws = 'mlbids') %>%
  janitor::clean_names() %>%
  dplyr::filter(!is.na(price)) %>%
  unique()

head(auction_result)

```

## Projection system data

```{r cache = TRUE, message = FALSE, results = 'hide'}

steamer <- get_steamer(2017) %>% proj_prep()

guru <- get_guru(2017) %>% proj_prep()

pecota <- get_pecota(file.path('..', 'projprep', 'paid_projections', 'pecota_2017.xls')) %>% proj_prep()

fp <- get_fantasy_pros(2017) %>% proj_prep()

```

## customize positions

manual position adjustments here

```{r}

#set the active projection system
active_pp <- steamer
#active_pp <- pecota
#active_pp <- fp

#MANUAL POSITION ELIGIBILITY ADJUSTMENTS!
manual_adjuster <- function(df, this_mlbid, position) {
  this_pos <- df[df$mlbid == this_mlbid, ]$position %>%
    strsplit(', ', fixed = TRUE) %>% unlist()
  
  if (!position %in% this_pos) {
    new_pos <- c(this_pos, position) %>% unique()
    new_pos <- paste(new_pos, collapse = ', ')
    df[df$mlbid == this_mlbid, 'position'] = new_pos
  }
  
  df
}

#czap is playing Ian Desmond at 1B
h_df <- manual_adjuster(active_pp$h_final, 435622, '1B')

#eric is playing Jose Ramirez at 
h_df <- manual_adjuster(h_df, 608070, '2B')

active_pp$h_final <- h_df

```


tag hit / pitch

```{r}

#load in the id map
data('id_map', package = 'projprep')

#tag pitcher / hitter
auction_tag <- auction_result %>%
  dplyr::left_join(id_map[, c('mlbid', 'pos')]) %>%
  dplyr::mutate(
    pos = ifelse(pos %in% c('SP', 'RP', 'P'), 'p', pos),
    pos = ifelse(pos %in% c('1B', '2B', '3B', 'C', 'CF', 'DH', 'LF', 'OF', 'RF', 'SS'), 'h', pos)
  )

auction_h <- auction_tag %>% dplyr::filter(pos == 'h')
auction_p <- auction_tag %>% dplyr::filter(pos == 'p')

```

## figure out where each guy starts

```{r}

new_cols <- c('mlbid', 'projection_name', 'value', 'position')

#add value and positions
auction_h <- auction_h %>% dplyr::inner_join(active_pp$h_final[, new_cols])
auction_p <- auction_p %>% dplyr::inner_join(active_pp$p_final[, new_cols])


#who starts where?
roster_h_pos <- c('C', 'SS', '3B', '2B', 'OF1', 'OF2', 'OF3', '1B', 'Util')
roster_p_pos <- c('RP1', 'RP2', 'RP3', 'SP1', 'SP2', 'SP3', 'P1', 'P2', 'P3')

for(i in roster_h_pos)
    auction_h[,i] <- NA

for(i in roster_p_pos)
    auction_p[,i] <- NA

```

### hitters
loop over each team and determine eligibility

```{r}

unq_owners <- auction_h$owner %>% unique()

elig_list <- list()

for (i in unq_owners) {
  print(i)
  this_team <- auction_h %>% dplyr::filter(owner == i)
  
  #loop over h_pos
  for (j in roster_h_pos) {
    clean_j <- gsub("\\d*$", "", j)
    print(clean_j)
    
    position_list <- lapply(this_team$position, function(x) strsplit(x, split = ', '))
    this_team[, j] <- lapply(position_list, function(x) grepl(clean_j, x)) %>% unlist()
    
    this_team[, 'Util'] <- TRUE
    
  }
  
  elig_list[[i]] <- this_team
}

elig_teams <- dplyr::bind_rows(elig_list)

head(elig_teams) %>% print.AsIs()

```

loop over each team and given eligibility, pick the best eligible guy

```{r}

best_list <- list()

for (i in unq_owners) {
  print(i)
  this_team <- elig_teams %>% dplyr::filter(owner == i)
  this_team$starting_pos <- NA
  
  #loop over h_pos
  for (j in roster_h_pos) {
  #for (j in c('C', 'SS', '3B', '2B', 'OF1', 'OF2')) {

    #build a logical vector of: is this player eligible at this position, AND are they
    #still unassigned as a starter
    this_team$mask <- unlist(this_team[, j]) & is.na(this_team$starting_pos)
    
    #rank inside that subset and record
    position_ranked <- rank(-this_team[this_team$mask, ]$value, ties.method = 'first')
    #I THINK I CAUGHT A DPLYR BUG!
    this_team[, j] = 0
    this_team[this_team$mask, j] = position_ranked
    
    #pick the #1 guy and mark his starting position
    this_team[this_team[, j] == 1, 'starting_pos'] = j
    
    this_team <- this_team %>% dplyr::select(-mask)
  }
    
  best_list[[i]] <- this_team
}

best_teams <- dplyr::bind_rows(best_list)

head(best_teams) %>% print.AsIs()

```




### pitchers
loop over each team and determine eligibility

```{r}

unq_owners <- auction_p$owner %>% unique()

elig_list_p <- list()

for (i in unq_owners) {
  print(i)
  this_team <- auction_p %>% dplyr::filter(owner == i)
  
  #loop over h_pos
  for (j in roster_p_pos) {
    clean_j <- gsub("\\d*$", "", j)
    print(clean_j)
    
    position_list <- lapply(this_team$position, function(x) strsplit(x, split = ', '))
    this_team[, j] <- lapply(position_list, function(x) grepl(clean_j, x)) %>% unlist()
    
    this_team[, 'P1'] <- TRUE
    this_team[, 'P2'] <- TRUE
    this_team[, 'P3'] <- TRUE
    
  }
  
  elig_list_p[[i]] <- this_team
}

elig_teams_p <- dplyr::bind_rows(elig_list_p)

head(elig_teams_p) %>% print.AsIs()

```

loop over each team and given eligibility, pick the best eligible guy

```{r}

best_list_p <- list()

for (i in unq_owners) {
  print(i)
  this_team <- elig_teams_p %>% dplyr::filter(owner == i)
  this_team$starting_pos <- NA
  
  #loop over h_pos
  for (j in roster_p_pos) {

    #build a logical vector of: is this player eligible at this position, AND are they
    #still unassigned as a starter
    this_team$mask <- unlist(this_team[, j]) & is.na(this_team$starting_pos)
    
    #rank inside that subset and record
    position_ranked <- rank(-this_team[this_team$mask, ]$value, ties.method = 'first')
    #I THINK I CAUGHT A DPLYR BUG!
    this_team[, j] = 0
    this_team[this_team$mask, j] = position_ranked
    
    #pick the #1 guy and mark his starting position
    this_team[this_team[, j] == 1, 'starting_pos'] = j
    
    this_team <- this_team %>% dplyr::select(-mask)
  }
    
  best_list_p[[i]] <- this_team
}

best_teams_p <- dplyr::bind_rows(best_list_p)

head(best_teams_p) %>% print.AsIs()

```

## Now score

```{r}

active_h <- best_teams %>%
  dplyr::filter(!is.na(starting_pos)) %>%
  dplyr::left_join(
    active_pp$h_final %>% dplyr::select(
      mlbid, ab, r, rbi, sb, tb, obp
    )
  ) %>%
  dplyr::mutate(
    pos = parse_factor(
      starting_pos, 
      c('C', '1B', '2B', 'SS', '3B', 'OF1', 'OF2', 'OF3', 'Util')
    )    
  )


active_p <- best_teams_p %>%
  dplyr::filter(!is.na(starting_pos)) %>%
  dplyr::left_join(
    active_pp$p_final %>% dplyr::select(
      mlbid, ip, w, sv, k, era, whip
    )
  ) %>%
  dplyr::mutate(
    pos = parse_factor(
      starting_pos, 
      c('SP1', 'SP2', 'SP3', 'RP1', 'RP2', 'RP3', 'P1', 'P2', 'P3')
    )    
  )

```

print each team - hitters

```{r}

h_sum_pipe <- . %>%
  dplyr::mutate(tob = ab * obp) %>%
  dplyr::summarize(
    ab = sum(ab),
    r = sum(r),
    rbi = sum(rbi),
    sb = sum(sb),
    tb = sum(tb),
    obp = sum(tob) / sum(ab)
  ) 

knitr_out <- list()

for (i in unq_owners) {
  
  this_owner <- active_h %>%
    dplyr::filter(owner == i)
  
  team_format <- this_owner %>%
    dplyr::select(owner, name, pos, projection_name, ab, r, rbi, sb, tb, obp) %>%
    dplyr::rename(
      player = name,
      system = projection_name
    ) %>%
    dplyr::arrange(pos)
  
  team_format_sum <- team_format %>%
    dplyr::mutate(player = 'total', pos = '') %>%
    dplyr::group_by(owner, player, pos, system) %>%
    h_sum_pipe() %>%
    dplyr::ungroup()
  
  team_format$pos <- as.character(team_format$pos)
  final <- rbind(team_format, team_format_sum)
  
  knitr_out[[i]] <- knitr::kable(final, digits = 3, format = 'markdown')
  
  print.AsIs(final, digits = 3)
  cat('\n')
}

```

```{r results='asis'}

for (i in knitr_out) {
  print(i)
}

```


print each team - pitchers

```{r}

p_sum_pipe <- . %>%
  dplyr::mutate(total_r = ip * era/9, total_wh = ip * whip) %>%
  dplyr::summarize(
    ip = sum(ip),
    w = sum(w),
    sv = sum(sv),
    k = sum(k),
    era = (sum(total_r) / sum(ip)) * 9,
    whip = sum(total_wh) / sum(ip)
  ) %>%
  dplyr::mutate(
    era = round(era, 2),
    whip = round(whip, 3)
  )

knitr_out_p <- list()

for (i in unq_owners) {
  
  this_owner <- active_p %>%
    dplyr::filter(owner == i)
  
  team_format <- this_owner %>%
    dplyr::select(owner, name, pos, projection_name, ip, w, sv, k, era, whip) %>%
    dplyr::rename(
      player = name,
      system = projection_name
    ) %>%
    dplyr::arrange(pos)
  
  team_format_sum <- team_format %>%
    dplyr::mutate(player = 'total', pos = '') %>%
    dplyr::group_by(owner, player, pos, system) %>%
    p_sum_pipe() %>%
    dplyr::ungroup()
  
  team_format$pos <- as.character(team_format$pos)
  final <- rbind(team_format, team_format_sum)
  
  knitr_out_p[[i]] <- knitr::kable(final, digits = 3, format = 'markdown')
  
  print.AsIs(final, digits = 3)
  cat('\n')
}

```

```{r results='asis'}

for (i in knitr_out_p) {
  print(i)
}

```

## fake hitting standings

```{r}

active_h_scored <- active_h %>%
  dplyr::group_by(owner, projection_name) %>%
  dplyr::rename(system = projection_name) %>%
  h_sum_pipe()

active_p_scored <- active_p %>%
  dplyr::group_by(owner, projection_name) %>%
  dplyr::rename(system = projection_name) %>%
  p_sum_pipe()

h_standings <- active_h_scored %>%
  dplyr::ungroup() %>%
  dplyr::mutate(
    r = rank(r, ties.method = 'min'),
    rbi = rank(rbi, ties.method = 'min'),
    sb = rank(sb, ties.method = 'min'),
    tb = rank(tb, ties.method = 'min'),
    obp = rank(obp, ties.method = 'min')
  ) %>%
  dplyr::rowwise() %>%
  dplyr::mutate(
    total_h = sum(r, rbi, sb, tb, obp)
  ) %>%
  dplyr::arrange(-total_h)

options(width = 100)

print(active_h_scored, digits = 3)

print(h_standings)
```

```{r}

knitr::kable(active_h_scored, digits = 3, format = 'markdown')

```

```{r}

knitr::kable(h_standings, format = 'markdown')

```


## fake pitching standings

```{r}

p_standings <- active_p_scored %>%
  dplyr::ungroup() %>%
  dplyr::mutate(
    w = rank(w, ties.method = 'min'),
    sv = rank(sv, ties.method = 'min'),
    k = rank(k, ties.method = 'min'),
    era = rank(-era, ties.method = 'min'),
    whip = rank(-whip, ties.method = 'min')
  ) %>%
  dplyr::rowwise() %>%
  dplyr::mutate(
    total_p = sum(w, sv, k, era, whip)
  ) %>%
  dplyr::arrange(-total_p)

print(active_p_scored, digits = 2)

print(p_standings)
```

```{r}

knitr::kable(active_p_scored, digits = 3, format = 'markdown')

```

```{r}

knitr::kable(p_standings, format = 'markdown')

```

## COMBINED FAKE STANDINGS

```{r}

all_team_stats <- active_h_scored %>% 
  dplyr::left_join(active_p_scored) %>%
  dplyr::select(-ab, -ip)

print.AsIs(all_team_stats, digits = 3)

all_standings <- h_standings %>%
  dplyr::left_join(p_standings) %>%
  dplyr::select(-ab, -ip) %>%
  dplyr::mutate(overall = total_h + total_p) %>%
  dplyr::arrange(-overall) 

print.AsIs(all_standings)
```


```{r}

knitr::kable(all_team_stats, digits = 3, format = 'markdown')

```

```{r}

knitr::kable(all_standings, format = 'markdown')

```
